---
title: "Secondary Axis Title"
output: html_document
---


Daytona testing git + github

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

To add a secondary axis title, use:

```{r}
scale_x_continuous(sec.axis = sec.axis(~ . , name = "XXX", breaks = NULL, labels = NULL))
```

One way to add an additional ribbon label with the name of a facetting variable(s), in addition to the primary facets labelled with the values of the facetting variable(s): 

df %>% 
  ggplot() +
  geom_point(aes(x = Xvar, y = Yvar), size = 0.1) +
  facet_grid(rows = vars(Groupvar1), cols = vars(Groupvar2)) +
  scale_y_continuous(sec.axis = sec_axis(~ . , name = sym("Groupvar1"), breaks = NULL, labels = NULL)) +
  scale_x_continuous(sec.axis = sec_axis(~ . , name = sym("Groupvar2"), breaks = NULL, labels = NULL))


To add a title to each facet, use:
XXX, YYY and ZZZ are entered as placeholders.
```{r}
ggh4x::facet_nested(cols = vars(XXX, YYY), rows = vars(ZZZ), labeller = labeller(YYY = label_both, XXX = label_value, ZZZ = label_both))
```

To change the angle of a facet header, use:

```{r}
theme(strip.text.x = element_text(angle = 45))
```
--------------------------------- Plots customizations including legend position (by SySl)-----------------------------

```{r}
df %>%
  ggplot() +
  geom_line(aes(x = Time_h, y = meanOD720_h, colour = as.factor(Strain)), size = 0.5, show.legend = T) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="") +
  labs(y = "Optical density ("~OD[720]~")", x = "Elapsed time (h)") +
  ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(), # remove minor grid lines
        panel.grid.major = element_blank(),  # remove major grid lines
        axis.text = element_text(size=12), # customize font size on x- and y- axis
        axis.title = element_text(size=16), # customize font size on x- and y- axis title
        strip.background = element_rect(fill="white"), # customize colour of facet strip (default gray when using "theme_bw")
        strip.text = element_text(size=12), # customize font size on the facets strip
        legend.background = element_rect(fill="transparent"), # customize colour of legend background 
        legend.position = c(0.12,0.96), # customize legend position 
        legend.text = element_text(size=11)) # customize font size on legend
```
