---
title: "Plot and Analyze microbial plate growth data"
author: "Douglas A. Campbell, Matt Tanton, Maximilian Berthold, Melissa L. Rioux"
date: "`r format(Sys.Date())`"
output:
  html_document:
    df_print: paged
---
ToDo
Add filtering variable values to .Rmd output

Set variables for project
```{r project data}
Project <- "salinity_growth"
FileIDSingle <- "Chl"
Replic <- "AllSal"
DataFolder <- "ProcessData"

#grouping variables for rows & columns, and for nesting for fitting
RowVar <- "salinity" #expected salinity
RowVar2 <- "CalcSal"
ColVar <- "strain"
NestVar <- "par_ue"
NestVarII <- "id"

#filtering variables
ChlAb = c("680", "720", "750")
Wavelength_nm <- c("680min720", "680min750", "680", "720", "750")
Par_ue = 300
nm_filter <- c("680min750")
#Strains <- c("CZS25K", "CZS48M", "PCC6803", "CCMP1333", "CCMP836", "NIES981")
Strains <- c( "CCMP1333")
StartDate <- c("20200828", "20201002", "20201005")
TissueTreated = FALSE
Media = "BG11+Na2CO3"
SourceSal = "4"
StopTime = 10

#fitting variable
FitVar <- "RegresChl_ugL"
#CorrOD RegresCellCount_mL RegresChl_ugL

```


```{r load libraries}
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(minpack.lm)
library(nlstools)
library(nlsMicrobio)
#library(OneR)
#source("CampbelLabRFunctions.txt")
```


```{r read data, warning=FALSE}
ImportGrowth <- readRDS(file = file.path(DataFolder,paste(Project,FileIDSingle, "GrowthLong.Rds", sep  = "_"),fsep = .Platform$file.sep))

#https://stackoverflow.com/questions/64111558/passing-variables-into-the-names-glue-parameter-of-tidyrpivot-wider

GrowthLong <- ImportGrowth %>%
  filter(Wavelength %in% nm_filter) #%>%
  # pivot_wider(id_cols = -c(OD, AvBlankOD), names_from = Wavelength, values_from = CorrOD, names_glue = "nm_{Wavelength}") %>% 
  # mutate("680min720" = nm_680 - nm_720, "680min750" = nm_680 - nm_750) %>%
  # pivot_longer(cols = c(nm_680, nm_720, nm_750, "680min720", "680min750"), values_to = "CorrOD", names_to = "Wavelength") %>%
  # mutate(Wavelength = str_remove(Wavelength, "nm_")) %>%
  # mutate(CorrOD = if_else(CorrOD < 0.001, 0.001, CorrOD)) #experimentally test to set values below 0.001 to 0.001 (~detection limit device)


GrowthLong <- GrowthLong %>%
  group_by(!!sym(NestVar), !!sym(RowVar2), !!sym(ColVar), !!sym(NestVarII), exp_date) %>%
  mutate(logFitVarminFitVar = log(!!sym(FitVar)/min(!!sym(FitVar), na.rm = TRUE))) %>% #problem with log leads to NaN, when value is very small
  ungroup() %>%
  mutate(strain = as.factor(strain))


```


```{r preplot}
GrowthLong %>%
  filter(strain %in% Strains) %>%
  filter(exp_date %in% StartDate) %>%
  #filter(exp_date == "20200902") %>%
  filter(Wavelength %in% Wavelength_nm) %>%
  #filter(tissue_treated_plate == TissueTreated) %>%
  #filter(media == Media) %>%
  #filter(SourceSal == source_salinity) %>%
  ggplot()+
  geom_point(aes(x = E_days, y = !!sym(FitVar), colour = as.factor(Wavelength))) +
  #coord_cartesian(ylim = c(0, 2)) +
  facet_grid(cols = vars(CalcSal), rows = vars(!!sym(NestVar))) +
    theme_bw() +
  labs(caption = paste(Wavelength_nm, "nm; PAR", Par_ue, "uE"))

```

```{r noise filtering}
#set filtering variables at top
#pick filtering option as either a simple threshold or a factor change between OD and OD_lead

#Screen_OD <- 2

FitData <- as_tibble(GrowthLong) %>%
  filter(strain %in% Strains) %>%
  filter(exp_date %in% StartDate) %>% #if multiple dates are applied, use %in% instead of ==
  filter(Wavelength %in% Wavelength_nm) %>%
  #filter(tissue_treated_plate == TissueTreated) %>%
  #filter(media == Media) %>%
  #filter(source_salinity == SourceSal) %>%
  group_by(well) %>%
  arrange(well, E_days) %>%
  mutate(FitVar_lead = lead(!!sym(FitVar), na.rm = TRUE)) %>%
  #filter(CorrOD < (OD_lead / Screen_OD)) %>%
  #filter(CorrOD < Screen_OD) %>%
  filter(E_days < StopTime)

test <- FitData %>%
  group_by(!!sym(NestVar), !!sym(RowVar), exp_date) %>%
  mutate(LagSeed = E_days[which.min(!!sym(FitVar))])
  
```


```{r filter plot}
FitData %>%
  filter(strain %in% Strains) %>%
  filter(exp_date %in% StartDate) %>%
  filter(Wavelength %in% Wavelength_nm) %>%
  #filter(tissue_treated_plate == TissueTreated) %>%
  filter(media == Media) %>%
  ggplot()+
  geom_point(aes(x = E_days, y = !!sym(FitVar), colour = as.factor(salinity))) +
  #coord_cartesian(ylim = c(0, 2)) +
  facet_grid(cols = vars(exp_date), rows = vars(!!sym(NestVar))) +
    theme_bw() +
  labs(caption = paste(Wavelength_nm, "nm; PAR", Par_ue, "uE"))
```


Define equations as functions.
x will be taken from 'E_days' when we run the fit.
```{r logistic_eqn}
LogisticEqn <- function(x, pmax, mu, intercept){(pmax*intercept*exp(mu*x))/(pmax + (intercept*(exp(mu*x)-1)))
}

# #not working properly
# loglag_eqn <- function(x, pmax, mu, intercept, lag){(pmax*intercept*exp(mu*(x-lag)))/(pmax + (intercept*(exp(mu*(x-lag))-1)))
# }
#natural log(RFU/min(RFU)); works, but confusing
ModGompertzEqn <- function(Amax,Amu,lag,x){(Amax*(exp(-exp((Amu*exp(1))/Amax*(lag-x)+1))))}
```



<!-- ```{r log fits} -->

<!-- MuStart = (log(max(FitData[FitData$Wavelength == Wavelength_nm, FitVar], na.rm = TRUE)) - log(min(FitData[FitData$Wavelength == Wavelength_nm, FitVar], na.rm = TRUE)))/max(FitData$E_days) -->

<!-- LogisticEqnStart<-list(pmax = max(FitData[FitData$Wavelength == Wavelength_nm, FitVar], na.rm = TRUE), mu = MuStart, intercept = min(FitData[FitData$Wavelength == Wavelength_nm, FitVar], na.rm = TRUE)) -->

<!-- LogisticEqnLower<-c((max(FitData[FitData$Wavelength == Wavelength_nm, FitVar], na.rm = TRUE) * 0.5),MuStart/10,((min(FitData[FitData$Wavelength == Wavelength_nm, FitVar], na.rm = TRUE) * 0.5))) -->

<!-- LogisticEqnUpper<-c((max(FitData[FitData$Wavelength == Wavelength_nm, FitVar], na.rm = TRUE) * 2),MuStart*2,((min(FitData[FitData$Wavelength == Wavelength_nm, FitVar], na.rm = TRUE) * 2))) -->

<!-- # loglag_eqn_start<-list(pmax = max(FitData[FitData$Wavelength == Wavelength_nm, FitVar], na.rm = TRUE), mu = 0.01, intercept = min(FitData[FitData$Wavelength == Wavelength_nm, FitVar], na.rm = TRUE), lag =0) -->
<!-- #  -->
<!-- # loglag_eqn_lower<-c((max(FitData[FitData$Wavelength == Wavelength_nm, FitVar], na.rm = TRUE) * 0.2),0.001,((min(FitData[FitData$Wavelength == Wavelength_nm, FitVar], na.rm = TRUE) * 0.8)),0) -->
<!-- #  -->
<!-- # loglag_eqn_upper<-c((max(FitData[FitData$Wavelength == Wavelength_nm, FitVar], na.rm = TRUE) * 2),0.1,((min(FitData[FitData$Wavelength == Wavelength_nm, FitVar], na.rm = TRUE) * 1.2)),24) -->

<!-- ModGompertzEqnStart<-list(Amax = max(FitData[FitData$Wavelength == Wavelength_nm, "logFitVarminFitVar"], na.rm = TRUE), Amu = MuStart, lag = 24) -->

<!-- ModGompertzEqnLower<-c((max(FitData[FitData$Wavelength == Wavelength_nm, "logFitVarminFitVar"], na.rm = TRUE) * 0.5),MuStart/10, 0) -->

<!-- ModGompertzEqnUpper<-c((max(FitData[FitData$Wavelength == Wavelength_nm, "logFitVarminFitVar"], na.rm = TRUE) * 2),MuStart*2,180) -->
<!-- ``` -->

<!-- Fit treatment specific logistic growth trajectories using nest purrr:map & broom::augment -->
<!-- ```{r treat growth} -->
<!-- TreatNest <- FitData %>% -->
<!--   nest(data = -c(!!sym(NestVar), !!sym(RowVar2), !!sym(RowVar), !!sym(ColVar), Wavelength)) -->

<!-- TreatLog <- TreatNest %>%  -->
<!--   mutate( -->
<!--   Fitlog = map(data, ~nlsLM(!!sym(FitVar) ~ LogisticEqn(x = E_days, pmax, mu, intercept), data = .x, start = LogisticEqnStart, lower = LogisticEqnLower, upper = LogisticEqnUpper)), -->
<!--   Predictlog = map(Fitlog ,augment), -->
<!--   Tidiedlog = map(Fitlog , tidy), -->
<!--   Paramlog = map(Fitlog , glance) -->
<!--   ) %>% -->
<!--    mutate( -->
<!--     FitGompertz = (map(data, ~nlsLM(logFitVarminFitVar ~ModGompertzEqn(x = E_days, Amax, Amu, lag), data = .x, start = ModGompertzEqnStart, lower = ModGompertzEqnLower, upper = ModGompertzEqnUpper))), -->
<!--     Predictgompertz = map(FitGompertz, augment), -->
<!--     Tidiedgompertz = map(FitGompertz, tidy), -->
<!--     Paramgompertz = map (FitGompertz, glance)) -->

<!-- TreatLogPredict <- TreatLog %>% -->
<!--   unnest(Predictlog) -->

<!-- TreatLogParam <- TreatLog %>%  -->
<!--   unnest(Tidiedlog) %>% -->
<!--   select(c(!!sym(NestVar), !!sym(RowVar2), !!sym(RowVar), !!sym(ColVar), Wavelength, term:p.value)) -->

<!-- TreatGompertzPredict <- TreatLog %>% -->
<!--   unnest(Predictgompertz) -->

<!-- TreatGompertzParam <- TreatLog %>%  -->
<!--   unnest(Tidiedgompertz) %>% -->
<!--   select(c(!!sym(NestVar), !!sym(RowVar2), !!sym(RowVar), !!sym(ColVar), Wavelength, term:p.value)) -->
<!-- ``` -->

<!-- Plot logistic & Modified Gompertz with Lag fits -->
<!-- ```{r TreatLogPlot gompertzplot} -->
<!-- TreatLogPlot <- TreatLogPredict %>%  -->
<!--   ggplot() +   -->
<!--   geom_line(aes(x = E_days, y = .fitted), size = 0.5) + -->
<!--   geom_point(aes(x = E_days, y = CorrOD), size = 0.6) + -->
<!--   # geom_ribbon(aes(x = E_days, ymin = (.fitted - .resid), ymax = (.fitted + .resid), alpha = 0.1),show.legend = FALSE) + -->
<!--   facet_grid(cols = vars(CalcSal), rows = vars(par_ue)) + -->
<!--   theme_bw() + -->
<!--   #theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.text = element_text(colour = "black")) + -->
<!--   # labs(y = expression(paste("OD"[`680 nm`])), x = "Elapsed time (h)", title = "Treatment Growth, Logistic Fits", subtitle = paste(str_c(Strains, collapse = "_"), str_c(StartDate, collapse = "_"))) -->
<!--   labs(y = "OD", -->
<!--        title = "Treatment Growth, Logistic Fits", -->
<!--        subtitle = paste(Wavelength_nm, "nm", str_c(Strains, collapse = "_"), str_c(StartDate, collapse = "_")), -->
<!--        caption = "Logistic line") -->

<!-- TreatLogPlot -->

<!-- TreatGompertzLagPlot <- TreatGompertzPredict %>%  -->
<!--   ggplot() +   -->
<!--   geom_line(aes(x = E_days, y = .fitted), size = 0.5) + -->
<!--   geom_point(aes(x = E_days, y = logFitVarminFitVar), size = 0.6) + -->
<!--   # geom_ribbon(aes(x = E_days, ymin = (.fitted - .resid), ymax = (.fitted + .resid), alpha = 0.1),show.legend = FALSE) + -->
<!--   facet_grid(cols = vars(CalcSal), rows = vars(par_ue)) + -->
<!--   theme_bw() + -->
<!--   #theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.text = element_text(colour = "black")) + -->
<!--   #labs(y = expression(paste("log(OD"[`680 nm`]*"/min OD"[`680 nm`]*")")), x = "Elapsed time (h)", title = "Treatment Growth, Modified Gompertz with Lag", subtitle = paste(str_c(Strains, collapse = "_"), str_c(StartDate, collapse = "_"))) -->
<!--   labs(y = "log(OD/minOD)", -->
<!--        title = "Treatment Growth, Modified Gompertz with Lag", -->
<!--        subtitle = paste(Wavelength_nm, "nm", str_c(Strains, collapse = "_"), str_c(StartDate, collapse = "_")), -->
<!--        caption = "Modified Gompertz with Lag Line") -->

<!-- TreatGompertzLagPlot -->
<!-- ``` -->


Fit treatment specific logistic growth trajectories using nest purrr:map & broom::augment using nest specific start, lower & upper settings extracted from each nest on the fly.
This may be necessary if the 'nests' contain diverse data patterns that fail to fit with generic start, lower & upper parameters extracted from the entire dataset

```{r treat growth specific}
#run nesting by passing in values of variables set at top; 
#!!sym(... allows nest to access the characters of the values passed in
TreatNestSpecific <- test %>%
  nest(data = -c(!!sym(NestVar), !!sym(RowVar2), !!sym(RowVar), !!sym(ColVar), Wavelength, LagSeed, exp_date))



#extract nest-specific start, lower & upper setting by passing in "."
TreatLogSpecific <- TreatNestSpecific %>% 
  mutate(
  FitLog = map(data, ~nlsLM(!!sym(FitVar) ~ LogisticEqn(x = E_days, Intercept, Mu, Pmax),
                            data = .x, 
                            start = list(Intercept = min(.[,FitVar], na.rm = TRUE), Mu = (log(max(.[, FitVar], na.rm = TRUE)) - log(min(.[ FitVar], na.rm = TRUE)))/max(.$E_days), Pmax = max(.[,FitVar], na.rm = TRUE)), 
                            lower = c((min(.[,FitVar], na.rm = TRUE) * 0.05), ((log(max(.[, FitVar], na.rm = TRUE)) - log(min(.[ FitVar], na.rm = TRUE)))/max(.$E_days)) *0.05, ((max(.[,FitVar], na.rm = TRUE)) * 0.05)),
                            upper = c((min(.[,FitVar], na.rm = TRUE) * 5), ((log(max(.[, FitVar], na.rm = TRUE)) - log(min(.[ FitVar], na.rm = TRUE)))/max(.$E_days)) * 5, ((max(.[,FitVar], na.rm = TRUE)) * 5)))),
  PredictLog = map(FitLog, augment),
  TidiedLog = map(FitLog, tidy),
  ParamLog = map(FitLog, glance)
  ) %>%
   mutate(
    FitGompertz = (map(data, ~nlsLM(logFitVarminFitVar ~ ModGompertzEqn(x = E_days, Lag, Gmu, Gmax),
                                    data = .x,
                                    start = list(Lag = LagSeed, Gmu = (log(max(.[, FitVar], na.rm = TRUE)) - log(min(.[ FitVar], na.rm = TRUE)))/max(.$E_days), Gmax = max(.[, "logFitVarminFitVar"], na.rm = TRUE)),
                                    lower = c(0, ((log(max(.[, FitVar], na.rm = TRUE)) - log(min(.[ FitVar], na.rm = TRUE)))/max(.$E_days)) * 0.01, max(.[, "logFitVarminFitVar"], na.rm = TRUE) * 0.01),
                                    upper = c(48, ((log(max(.[, FitVar], na.rm = TRUE)) - log(min(.[ FitVar], na.rm = TRUE)))/max(.$E_days)) * 1.5, max(.[, "logFitVarminFitVar"], na.rm = TRUE) * 1.5)))),
    PredictGompertz = map(FitGompertz, augment),
    TidiedGompertz = map(FitGompertz, tidy),
    ParamGompertz = map (FitGompertz, glance))

TreatLogSpecificPredict <- TreatLogSpecific %>%
  unnest(PredictLog)

TreatLogSpecificCoeff <- TreatLogSpecific %>% 
  unnest(TidiedLog) %>%
  dplyr::select(c(!!sym(NestVar), !!sym(RowVar2), !!sym(RowVar), !!sym(ColVar), Wavelength, term:p.value))

TreatGompertzSpecificPredict <- TreatLogSpecific %>%
  unnest(PredictGompertz)

TreatGompertzSpecificCoeff <- TreatLogSpecific %>% 
  unnest(TidiedGompertz) %>%
  dplyr::select(c(!!sym(NestVar), !!sym(RowVar2), !!sym(RowVar), !!sym(ColVar), Wavelength, term:p.value))
```


```{r}
CheckDate <- StartDate %>%
  as_data_frame(StartDate) %>%
  slice(1)

TreatLogSpecificPlot <- TreatLogSpecificPredict %>% 
  filter(exp_date %in% CheckDate) %>%
  filter(Wavelength %in% nm_filter) %>%
  ggplot() +  
  geom_line(aes(x = E_days, y = .fitted), size = 0.5) +
  geom_point(aes(x = E_days, y = !!sym(FitVar)), size = 0.6) +
  # geom_ribbon(aes(x = E_days, ymin = (.fitted - .resid), ymax = (.fitted + .resid), alpha = 0.1),show.legend = FALSE) +
  facet_grid(cols = vars(CalcSal), rows = vars(par_ue)) +
  theme_bw() +
  #theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.text = element_text(colour = "black")) +
  #labs(y = expression(paste("log(OD"[`680 nm`]*"/min OD"[`680 nm`]*")")), x = "Elapsed time (h)", title = "Treatment Growth, Modified Gompertz with Lag", subtitle = paste(str_c(Strains, collapse = "_"), str_c(StartDate, collapse = "_")))
  labs(y = FitVar,
       title = "Treatment Growth, Specific Log",
       subtitle = paste(nm_filter, "nm", str_c(Strains, collapse = "_"), str_c(StartDate, collapse = "_")),
       caption = "Log")

TreatLogSpecificPlot

TreatGompertzLagSpecificPlot <- TreatGompertzSpecificPredict %>% 
  filter(exp_date %in% CheckDate) %>%
  filter(Wavelength %in% nm_filter) %>%
  ggplot() +  
  geom_line(aes(x = E_days, y = .fitted), size = 0.5) +
  geom_point(aes(x = E_days, y = logFitVarminFitVar), size = 0.6) +
  # geom_ribbon(aes(x = E_days, ymin = (.fitted - .resid), ymax = (.fitted + .resid), alpha = 0.1),show.legend = FALSE) +
  facet_grid(cols = vars(CalcSal), rows = vars(par_ue)) +
  theme_bw() +
  #theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.text = element_text(colour = "black")) +
  #labs(y = expression(paste("log(OD"[`680 nm`]*"/min OD"[`680 nm`]*")")), x = "Elapsed time (h)", title = "Treatment Growth, Modified Gompertz with Lag", subtitle = paste(str_c(Strains, collapse = "_"), str_c(StartDate, collapse = "_")))
  labs(y = FitVar,
       title = "Treatment Growth, Modified Gompertz Specific with Lag",
       subtitle = paste(nm_filter, "nm", str_c(Strains, collapse = "_"), str_c(StartDate, collapse = "_")),
       caption = "Modified Gompertz with Lag Line")

TreatGompertzLagSpecificPlot
```


```{r save plots}
# ggsave(filename = file.path("Plots", paste(Project, Replic, 
# FileIDSingle, str_c(Strains, collapse = "_"), str_c(StartDate, collapse = "_"),"TreatLogPlot.png", sep = "_"),fsep = .Platform$file.sep ), plot = TreatLogPlot, height = 4, width = 6)
# 
# ggsave(filename = file.path("Plots", paste(Project, Replic, 
# FileIDSingle, str_c(Strains, collapse = "_"), str_c(StartDate, collapse = "_"), "TreatGompertzLagPlot.png", sep = "_"),fsep = .Platform$file.sep ), plot = TreatGompertzLagPlot, height = 4, width = 6)
```

Display & save parameters of logistic & modified Gompertz with lag.
```{r fit parameters}
TreatLogSpecificCoeff %>%
  mutate_if(is.numeric, round, digits = 3)

TreatGompertzSpecificCoeff %>%
  mutate_if(is.numeric, round, digits = 3)

#save .rds of the current round of fit parameters
saveRDS(TreatLogSpecificCoeff, file = file.path(DataFolder,paste(Project,FileIDSingle, Replic, "TreatLogSpecificCoeff", str_c(Strains, collapse = "_"), "ChlAb", ".Rds",sep = "_"),fsep = .Platform$file.sep))

#, str_c(StartDate, collapse = "_") add, if not all replicates are run at once

saveRDS(TreatGompertzSpecificCoeff, file = file.path(DataFolder,paste(Project,FileIDSingle, Replic, "TreatGompSpeCo", str_c(Strains, collapse = "_"), "ChlAb", ".Rds",sep = "_"),fsep = .Platform$file.sep))

#append current round of logistic fit parameters to growing .csv
#Be Careful: Running the same data multiple time will continue to append to growing .csv

# write_csv(TreatLogSpecificCoeff, path =  file.path(Project, DataFolder, paste(FileIDSingle, Replic, "TreatLogSpecificCoeff.csv",sep = "_"),fsep = .Platform$file.sep), col_names = TRUE, append = TRUE)
# 
# write_csv(TreatGompertzSpecificCoeff, path =  file.path(Project, DataFolder, paste(FileIDSingle, Replic, "TreatGompSpeCo.csv",sep = "_"),fsep = .Platform$file.sep), col_names = TRUE, append = TRUE)
```


Fit and plot treatment id specific (well or tube) growth trajectories using nest purrr:map & broom::augment

Not Working; issue with data?
```{r well growth}
# well_nest <- as_tibble(GrowthLong) %>%
#   filter(strain %in% c("CCMP1333", "PCC8806")) %>%
#   filter(Wavelength == Wavelength_nm) %>%
#   nest(-c(!!sym(NestVar), !!sym(RowVar), !!sym(ColVar), !!sym(NestVarII)))
# 
# 
# well_log <- well_nest %>% 
#   mutate(
#   fit = map(data, ~nlsLM(!!sym(FitVar) ~ logistic_eqn(x = E_days, pmax, mu, intercept), data = .x, start = LogisticEqnStart, lower = LogisticEqnLower, upper = LogisticEqnUpper)),
#   predict = map(fit,augment),
#   tidied = map(fit, tidy),
#   param = map(fit, glance)
#   )
# 
# well_log_predict <-  well_log %>%
#   unnest(predict)
#   
# well_log_param <- well_log %>%
#   mutate(OD = map(data, "OD", data = .x),
#   relmax = map(OD, ~mean(order(-.x)[1:3]/mean(order(.x)[1:3])))) %>%
#   mutate(relmax = as.numeric(relmax)) %>%
#   unnest(tidied) %>%
#   select(-c(data, fit, predict, param, OD))
# 
# WellLogPlot <- well_log_predict %>% 
#   filter(par_ue == Par_ue) %>%
#   ggplot() +  
#   geom_line(aes(x = E_days, y = .fitted,colour = !!sym(NestVarII)), size = 0.5) +
#   geom_point(aes(x = E_days, y = OD, colour = !!sym(NestVarII)), size = 0.1) +
# geom_ribbon(aes(x = E_days, ymin = (.fitted - .resid), ymax = (.fitted + .resid), alpha = 0.1),show.legend = FALSE) +
#   facet_grid(cols = vars(salinity), rows = vars(strain)) +
#   theme_bw() +
#   labs(y = "OD",
#        title = "Well Growth, Logistic Fits",
#        subtitle = paste(Wavelength_nm, "_nm",
# Par_ue, "_uE"),
#        caption = "Logistic line, residuals grey ribbon")
# 
# WellLogPlot
# 
# ggsave(filename = file.path("plots", paste(Project, 
# FileIDSingle, "WellLogPlot.png", sep = "_"),fsep = .Platform$file.sep ), plot = WellLogPlot)
# 
# #parameters of colony specific logistic fits
# well_log_param %>%
#   mutate_if(is.numeric, round, digits = 2)
# 
# saveRDS(well_log_predict, file = file.path("process_data",paste(Project,FileIDSingle, "well_log_predict", Wavelength_nm, ".Rds",sep = "_"),fsep = .Platform$file.sep))
# 
# saveRDS(well_log_param, file = file.path("process_data",paste(Project,FileIDSingle, "well_log_param", Wavelength_nm, ".Rds",sep = "_"),fsep = .Platform$file.sep))
```