---
title: "MultiDataProcessLogWW"
author:
- Laurel Genge
- Carlie Barnhill
- Max Berthold
- Douglas A. Campbell
- Mireille Savoie
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: Prochlorococcus_O2_NPQ.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

## Set figure caption font size
```{css, echo=FALSE}
p.caption {
  font-size: 18px;
}
```

## Set Chunk Options
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

Implement logistic and other growth curve fits to MultiCulti growth trajectories.

# Load Libraries and set project variables
Run only first time in session


```{r load libraries}
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(zoo)
#library(tidyquant)
#library(data.table)
#library(googledrive)
#library(googlesheets4)
library(minpack.lm)
#library(dplyr)

#attach psych for harmonic.mean() for averaging rates
#library(psych)
library(RcppRoll)  #used for rolling mean
```

Run only first time in session

```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..","ImportedData")
PlotsPath <- file.path("..","Plots")
DataOut <- file.path("..","ProcessedData", "LogGrowthFits")
MetaCatalog <- file.path("..","PicoCatalog.csv")

TruncFactor <- 0.5

GrowthFlagError <- 0.1

Sensor <- "od-680"


#set the hour of day at which photoperiod starts for later generation of ToD Time of Day
#replaced by extraction of StartHour from first row of data file in MultiDataImport.Rmd
#StartHour <- 6
#EndHour <- 18

```

Run only first time in session

```{r set colours}
MyWavelengths = c(405, 450, 475, 530, 615, 660, 730, "WW")
MCMIXColours = c("violet", "darkblue", "dodgerblue", "green","orange","red","purple", "black")

names(MCMIXColours) <- MyWavelengths
MCMIXColours
```



# List previously processed files

Run only first time in session

```{r previously processed files}
list.files(path = DataOut, pattern = Project, full.names = TRUE)

```

# List available tidied, organized .Rds files of MultiCulti data.

Exported from runs of MultiDataImport.Rmd Run only first time in session

```{r list tidied data files}
list.files(path = DataIn, pattern = Project, full.names = TRUE)

```

# Select and Read ProcessFile

Run for each file in a session; all chunks below run for each file.

Moving this template to a working project folder will need editing of this file path to a relative path within the project folder.
```{r read ProcessFile}
ProcessFile <- "~/Dropbox/Pico/ImportedData/20220125_PICO_MCMIX004_RUN47_TargetDataMetaFilter.Rds"

ProcessFileName <- str_split(string = ProcessFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") %>%
  str_remove(pattern = "_TargetDataMetaFilter")

ProcessData <- readRDS(ProcessFile)  %>%
  ungroup()

colnames(ProcessData)
```

Remove extraneous columns from ProcessData; could have been done at end of MultiDataImport.Rmd
```{r clean up ProcessData}
ProcessData <- ProcessData %>%
  #select(-contains("actinic-lights.light")) %>%
  select(-c("Plate", "Well", "MovAvg680", "MovAvg720",  "IsMovAvgOutlier680", "IsMovAvgOutlier720","ActinicMin_parOD680",          
"ActinicMid_parOD680", "ActinicMin_parOD720", "ActinicMid_intervalOD720" ))

colnames(ProcessData)

```

Add deltaOD columns; filter for failed ln; add lognorm columns; add lagseed for each tube
```{r add columns for fitting}
ProcessData <- ProcessData %>%
  #drop_na(Tube, MC, ExpDate) %>%
  mutate(deltaOD = OD680 - OD720) %>%
  # Script fails at line 149 for WL runs, MC column are all NAs so all data is filtered out
  filter(!is.infinite(log(OD720))) %>%
  filter(!is.infinite(log(OD680))) %>%
  filter(!is.infinite(log(deltaOD))) %>%
  filter(!is.nan(log(OD720))) %>%
  filter(!is.nan(log(OD680))) %>%
  filter(!is.nan(log(deltaOD)))



#lognormOD720 and deltaOD for Gompe
#using RcppRoll functions to find the minimum of a 5 point window to lower noise in normalizations
ProcessData <- ProcessData %>%
  group_by(Tube) %>%
  mutate(rollmeanOD720 = roll_mean(OD720, n = 5, align = "left", fill = NA),
         rollmeandeltaOD = roll_mean(deltaOD, n = 5, align = "left", fill = NA),
         lognormOD720 = log(OD720/min(rollmeanOD720, na.rm = TRUE)),
         lognormdeltaOD = log(deltaOD/min(deltaOD, na.rm = TRUE))) %>%
  mutate(LagSeedOD720 = time[which.min(rollmeanOD720)],
         LagSeeddeltaOD = time[which.min(rollmeanOD720)]
         ) %>%
  ungroup()

```


# Generate a plot of the data in the selected tidied MultiCulti file.

```{r prelim ProcessPlot}
#Run <- c("MultiCulti/20200124_PICO_MCMIX004_RUN1.csv", "MultiCulti/20200124_PICO_MCMIX006_RUN2.csv")

ProcessData %>%
  ggplot() +
  geom_point(aes(x = time, y = OD720), size = 0.1) +
  geom_point(aes(x = time, y = Actinic_par/1000, colour = as.factor(WL)), size = 0.05) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
  theme_bw()

ProcessData %>%
  #filter(Tube == 5) %>%
  ggplot() +
  geom_point(aes(x = time, y = log(OD720)), size = 0.1) +
  geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
  geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
  theme_bw()

ProcessData %>%
 # filter(Tube == 1) %>%
  ggplot() +
  geom_point(aes(x = time, y = deltaOD), size = 0.1) +
  #geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
  theme_bw()

ProcessData %>%
 # filter(Tube == 1) %>%
  ggplot() +
  geom_point(aes(x = time, y = lognormOD720), size = 0.1) +
  #geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
  theme_bw()

ProcessData %>%
 # filter(Tube == 1) %>%
  ggplot() +
  geom_point(aes(x = time, y = lognormdeltaOD), size = 0.1) +
  #geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
  theme_bw()

```

# For split files only; select the interval that covers before the change in actinic light
```{r Interval Data for split files}
#even multiples of 24 + StartHour to start at photoperiod
# LowerTime <- 24 * 0
# UpperTime <- 24 * 17
# #
# ProcessData <- ProcessData %>%
#   filter(time <= UpperTime)
```


# Attempt  Fits of Data
Create R function for logistic equation.
Check with Max for alternate formulations that include lag?
Consider which parameter(s) to report for comparison(s) of strain responses to growth conditions
  -mu
  -Pmax
  -other...
```{r fitting functions, message = FALSE}
#define a logistic equation as a function.
#x will be taken from 'time' when we run the fit.
logistic_eqn <- function(x, Lmax, Lmu, Lintercept){(Lmax*Lintercept*exp(Lmu*x))/(Lmax + (Lintercept*(exp(Lmu*x)-1)))
}
#Modified Gompertz equation
ModGompertzEqn <- function(x,GLag,Gmax,Gmu){(Gmax*(exp(-exp((Gmu*exp(1))/Gmax*(GLag-x)+1))))}

# Exponential equation 
exp_eqn <- function(x, Emu, Eintercept){(Eintercept*exp(x*Emu))}

#Estimate amplitude of growth
growth_amp <- function(y){(max(as.numeric(y), na.rm = TRUE) - min(as.numeric(y), na.rm = TRUE))/min(as.numeric(y), na.rm = TRUE)}

bob <- c(1,2,4,5,6,7)

growth_amp(y = bob)


```




```{r nested regressions }

ProcessDataNestGrowth  <- ProcessData %>%
  filter(lognormdeltaOD > 0) %>%
  filter(lognormOD720 > 0) %>%
nest(tubedata = c(time, abs_time, ToD, Day, Actinic_par, OD680, OD720, deltaOD, ActinicMid_parOD720, ActinicMid_dayOD720,rollmeanOD720,rollmeandeltaOD,lognormOD720, lognormdeltaOD, LagSeedOD720, LagSeeddeltaOD)) %>%
  mutate(OD720_logistic = map(tubedata, possibly(~nlsLM(OD720 ~ logistic_eqn(x = time, Lmax, Lmu, Lintercept),
                            data = .x,
                            start = list(Lmax = max(.$OD720, na.rm = TRUE),  Lmu = (log(max(.$OD720, na.rm = TRUE)) - log(min(.$OD720, na.rm = TRUE)))/max(.$time), Lintercept = min(.$OD720, na.rm = TRUE)),
                            control = list(maxiter = 500)), otherwise = NULL)),
         OD720_logistic_tidied =  map(OD720_logistic, possibly(tidy, otherwise = NULL)),
         OD720_logistic_param = map(OD720_logistic,possibly(glance, otherwise = NULL))
         ) %>%
  mutate(deltaOD_logistic = map(tubedata, possibly(~nlsLM(deltaOD ~ logistic_eqn(x = time, Lmax, Lmu, Lintercept),
                            data = .x,
                            start = list(Lmax = max(.$deltaOD, na.rm = TRUE),  Lmu = (log(max(.$deltaOD, na.rm = TRUE)) - log(min(.$deltaOD, na.rm =  TRUE)))/max(.$time), Lintercept = min(.$deltaOD, na.rm = TRUE)),
                            control = list(maxiter = 500)), otherwise = NULL)),
         deltaOD_logistic_tidied =  map(deltaOD_logistic, possibly(tidy, otherwise = NULL)),
         deltaOD_logistic_param = map(deltaOD_logistic,possibly(glance, otherwise = NULL)),
         ) %>%
  mutate(LogFlag_OD720 = if_else(OD720_logistic != "NULL", 1, 0),
         LogFlag_deltaOD = if_else(deltaOD_logistic != "NULL", 1, 0)
         ) %>%
  mutate(lognormOD720_Gompertz = map(tubedata, possibly(~nlsLM(lognormOD720 ~ ModGompertzEqn(x = time, GLag, Gmax, Gmu),
                                    data = .x,
                                    start = list(GLag = .$LagSeedOD720[1], Gmu = (log(max(.$lognormOD720, na.rm = TRUE)) - log(min(.$lognormOD720, na.rm = TRUE)))/max(.$time), Gmax = max(.$lognormOD720, na.rm = TRUE)),
                                   control = list(maxiter = 500)), otherwise = NULL)),
         lognormOD720_Gompertz_tidied =  map(lognormOD720_Gompertz, possibly(tidy, otherwise = NULL)),
         lognormOD720_Gompertz_param = map(lognormOD720_Gompertz,possibly(glance, otherwise = NULL))
        ) %>%
 mutate(lognormdeltaOD_Gompertz = map(tubedata, possibly(~nlsLM(lognormdeltaOD ~ ModGompertzEqn(x = time, GLag, Gmax, Gmu),
                                    data = .x,
                                    start = list(GLag = .$LagSeeddeltaOD[1], Gmu = (log(max(.$lognormdeltaOD, na.rm = TRUE)) - log(min(.$lognormdeltaOD, na.rm = TRUE)))/max(.$time), Gmax = max(.$lognormdeltaOD, na.rm = TRUE)),
                                   control = list(maxiter = 500)), otherwise = NULL)),
         lognormdeltaOD_Gompertz_tidied =  map(lognormdeltaOD_Gompertz, possibly(tidy, otherwise = NULL)),
         lognormdeltaOD_Gompertz_param = map(lognormdeltaOD_Gompertz,possibly(glance, otherwise = NULL))
        ) %>%
    mutate(GrowthAmpdeltaOD = map(tubedata, ~growth_amp(y = .$rollmeandeltaOD)),
           GrowthAmpOD720 = map(tubedata, ~growth_amp(y = .$rollmeanOD720))
    )
```


```{r test fits}
testamp <- ProcessData %>%
  filter(lognormdeltaOD > 0) %>%
  filter(lognormOD720 > 0) %>%
nest(tubedata = c(time, abs_time, ToD, Day, Actinic_par, OD680, OD720, deltaOD, ActinicMid_parOD720, ActinicMid_dayOD720,rollmeanOD720,rollmeandeltaOD,lognormOD720, lognormdeltaOD, LagSeedOD720, LagSeeddeltaOD)) %>%
  mutate(GrowthAmpdeltaOD = map(tubedata, ~growth_amp(y = .$rollmeandeltaOD)))
  

```


 


```{r plot logistics predictions}
#improve with automated annotate placement based upon data traces; difficulty is that data is nested until expansion for ggplot b/c we need to conserve memory so data traces are not easily accessible
# segmentYstart <- as.numeric(IntervalDataTube1[IntervalDataTube1$time == 52, "lnOD680"])
# segmentYend <- as.numeric(IntervalDataTube1[IntervalDataTube1$time == 54, "lnOD680"])

OD_x = 150
OD_y = 0.15

Par_x = 350
Par_y = 0.04

Resid_x = 80
Resid_y = -0.03

Predict_x = 90
Predict_y = 0.06

#predictions of condition specific fits
ProcessDataNestGrowth %>%
  #drop_na(OD720_logistic) %>%
  mutate(OD720_logistic_predict = map(OD720_logistic, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(tubedata, OD720_logistic_predict),names_sep = "_", keep_empty = TRUE) %>%
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_OD720), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
 # geom_text(data = . %>% filter(GrowthFlag_OD720 == 0), aes(x = 200, y = 0.2, label = "*"), size = 5) +
  geom_point(aes(x = tubedata_time, y = OD720_logistic_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = tubedata_time, y = OD720_logistic_predict_.resid), colour = "red", size = 0.05) +geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/1000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
  #coord_cartesian(xlim = c(-5, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  labs(subtitle = "Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "Optical Density 720nm (OD720)", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")


ProcessDataNestGrowth %>%
  #drop_na(OD720_logistic) %>%
  filter(Tube == 1) %>%
  mutate(OD720_logistic_predict = map(OD720_logistic, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(tubedata, OD720_logistic_predict),names_sep = "_") %>%
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_OD720), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = tubedata_time, y = OD720_logistic_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = tubedata_time, y = OD720_logistic_predict_.resid), colour = "red", size = 0.05) + 
  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/1000, colour = as.factor(WL)), size = 0.1, alpha = 0.1) +
  #coord_cartesian(xlim = c(-5, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  annotate(geom = "text", x = OD_x, y = OD_y, label = "OD720", size = 5, colour = "darkgreen") +
  annotate(geom = "text", x = Par_x, y = Par_y, label = "Light level", size = 5, colour = "darkblue") +
  annotate(geom = "text", x = Resid_x, y = Resid_y, label = "Model residuals", size = 5, colour = "red") +
  annotate(geom = "text", x = Predict_x, y = Predict_y, label = "Logistic Regression", size = 5, colour = "black") +
  #7_cartesian(xlim = c(-5, 255)) +
  labs(subtitle = "Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "Optical Density 720nm (OD720)", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")


ProcessDataNestGrowth %>%
  #drop_na(deltaOD_logistic) %>%
  mutate(deltaOD_logistic_predict = map(deltaOD_logistic, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(tubedata, deltaOD_logistic_predict),names_sep = "_", keep_empty = TRUE) %>%
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_deltaOD), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  #geom_text(data = . %>% filter(GrowthFlag_deltaOD == 0), aes(x = 200, y = 0.2, label = "*"), size = 5) +
  geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.resid), colour = "red", size = 0.05) + geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/1000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
  #coord_cartesian(xlim = c(-5, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  labs(subtitle = "Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "Delta Optical Density (deltaOD)", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")


ProcessDataNestGrowth %>%
  #drop_na(deltaOD_logistic) %>%
  filter(Tube == 1) %>%
  mutate(deltaOD_logistic_predict = map(deltaOD_logistic, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(tubedata, deltaOD_logistic_predict),names_sep = "_") %>%
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_deltaOD), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.resid), colour = "red", size = 0.05) + 
  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/1000, colour = as.factor(WL)), size = 0.5, alpha = 0.1) +
  #coord_cartesian(xlim = c(0, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  annotate(geom = "text", x = OD_x, y = OD_y, label = "deltaOD", size = 5, colour = "darkgreen") +
  annotate(geom = "text", x = Par_x, y = Par_y, label = "Light level", size = 5, colour = "darkblue") +
  annotate(geom = "text", x = Resid_x, y = Resid_y, label = "Model residuals", size = 5, colour = "red") +
  annotate(geom = "text", x = Predict_x, y = Predict_y, label = "Logistic Regression", size = 5, colour = "black") +
  labs(subtitle = "Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName , y = "Delta Optical Density (deltaOD)", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")


# ProcessDataNestGrowth %>%
#   #drop_na(OD720trunc_logistic) %>%
#   #filter(Tube == 1) %>%
#   mutate(OD720trunc_logistic_predict = map(OD720trunc_logistic, possibly(augment, otherwise = NULL))) %>%
#   unnest(cols = c(OD720trunc_logistic_predict), names_sep = "_", keep_empty = TRUE) %>%
#   ggplot() +
#   geom_point(aes(x = OD720trunc_logistic_predict_time, y = OD720trunc_logistic_predict_OD720), colour = "darkgreen", size = 0.1) +
#   scale_colour_manual(values = MCMIXColours) +
#  # geom_text(data = . %>% filter(GrowthFlag_OD720 == 0), aes(x = 200, y = 0.2, label = "*"), size = 5) +
#   geom_point(aes(x = OD720trunc_logistic_predict_time, y = OD720trunc_logistic_predict_.fitted), colour = "black", size = 0.1) +
#   geom_point(aes(x = OD720trunc_logistic_predict_time, y = OD720trunc_logistic_predict_.resid), colour = "red", size = 0.05) + #geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/1000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
#   #coord_cartesian(xlim = c(-5, 675)) +
#   #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
#   facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
#   labs(subtitle = "Truncated- Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "Optical Density 720nm (OD720)", x = "Elapsed Time (h)") +
#   theme_bw() +
#   labs(colour = "Actinic PAR (nm)")


ProcessDataNestGrowth %>%
  mutate(lognormOD720_Gompertz_predict = map(lognormOD720_Gompertz, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(tubedata, lognormOD720_Gompertz_predict),names_sep = "_", keep_empty = TRUE) %>%
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_lognormOD720), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = tubedata_time, y = lognormOD720_Gompertz_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = tubedata_time, y = lognormOD720_Gompertz_predict_.resid), colour = "red", size = 0.05) +geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/1000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
  #coord_cartesian(xlim = c(-5, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  labs(subtitle = "lognormOD720_Gompertz; Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "lognormOD720", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")


ProcessDataNestGrowth %>%
  mutate(lognormdeltaOD_Gompertz_predict = map(lognormdeltaOD_Gompertz, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(tubedata, lognormdeltaOD_Gompertz_predict),names_sep = "_", keep_empty = TRUE) %>%
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_lognormdeltaOD), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = tubedata_time, y = lognormdeltaOD_Gompertz_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = tubedata_time, y = lognormdeltaOD_Gompertz_predict_.resid), colour = "red", size = 0.05) +geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/1000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
  #coord_cartesian(xlim = c(-5, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  labs(subtitle = "lognormdeltaOD_Gompertz; Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "lognormdeltaOD", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")





```

```{r save logistic model plots}
# ggsave(file = file.path(PlotsPath, paste(ProcessFileName, "OD720LogGrowthPlot",".png",sep = "")), plot = OD720LogGrowthPlot, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
# 
# ggsave(file = file.path(PlotsPath, paste(ProcessFileName, "OD720LogGrowthPlotExpand",".png",sep = "")), plot = OD720LogGrowthPlotExpand, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
# 
# ggsave(file = file.path(PlotsPath, paste(ProcessFileName, "DeltaODLogGrowthPlot",".png",sep = "")), plot = DeltaODLogGrowthPlot, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
# 
# ggsave(file = file.path(PlotsPath, paste(ProcessFileName, "DeltaODLogGrowthPlotExpand",".png",sep = "")), plot = DeltaODLogGrowthPlotExpand, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)

```

```{r exclude poor fits}
# TestProcessDataNestGrowth %>%
#   filter(Tube != 4
```



```{r logistic fit terms}
# GrowthFlagError defined at start
OD720LogisticTerms <- ProcessDataNestGrowth %>%
 unnest(cols = c(OD720_logistic_tidied),names_sep = "_") %>%
  select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, OD720_logistic_tidied_term, OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error)) %>%
  pivot_wider(names_from =  OD720_logistic_tidied_term, values_from = c(OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error), names_sep = "_") %>%
  rename(OD720_Lmax = OD720_logistic_tidied_estimate_Lmax,
         OD720_Lmax_se = OD720_logistic_tidied_std.error_Lmax,
         OD720_Lmu = OD720_logistic_tidied_estimate_Lmu,
         OD720_Lmu_se = OD720_logistic_tidied_std.error_Lmu,
         OD720_Lintercept = OD720_logistic_tidied_estimate_Lintercept,
         OD720_Lintercept_se = OD720_logistic_tidied_std.error_Lintercept) %>%
  mutate(GrowthFlag = if_else((OD720_Lintercept + OD720_Lintercept_se) < ((OD720_Lmax - OD720_Lmax_se) & (OD720_Lmu_se < OD720_Lmu * GrowthFlagError) & (OD720_Lmax_se < OD720_Lmax * GrowthFlagError) ), 1, 0))



```

Plot Logistic Fit Terms vs. conditions
```{r logistic fit terms plot}
ProcessDataNestGrowth %>%
 unnest(cols = c(OD720_logistic_tidied),names_sep = "_") %>%
  select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, OD720_logistic_tidied_term, OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error)) %>%
  pivot_wider(names_from =  OD720_logistic_tidied_term, values_from = c(OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error), names_sep = "_") %>%
  rename(OD720_Lmax = OD720_logistic_tidied_estimate_Lmax,
         OD720_Lmax_se = OD720_logistic_tidied_std.error_Lmax,
         OD720_Lmu = OD720_logistic_tidied_estimate_Lmu,
         OD720_Lmu_se = OD720_logistic_tidied_std.error_Lmu,
         OD720_Lintercept = OD720_logistic_tidied_estimate_Lintercept,
         OD720_Lintercept_se = OD720_logistic_tidied_std.error_Lintercept) %>%
  mutate(GrowthFlag = if_else((OD720_Lintercept + OD720_Lintercept_se) < ((OD720_Lmax - OD720_Lmax_se) & (OD720_Lmu_se < OD720_Lmu * GrowthFlagError) & (OD720_Lmax_se < OD720_Lmax * GrowthFlagError) ), 1, 0)) %>%
  filter(GrowthFlag != 0) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = OD720_Lmu, colour = as.factor(WL))) +
  #geom_text(data = . %>% filter(GrowthFlag_OD720 == 0), aes(x = Par_ue, y = 0, label = "*")) +
  geom_errorbar(aes(x = Par_ue, ymin = OD720_Lmu - OD720_Lmu_se, ymax = OD720_Lmu + OD720_Lmu_se, colour = as.factor(WL))) + 
  scale_colour_manual(values = MCMIXColours) +
  facet_grid (cols = vars(Strain), rows = vars(O2)) +
  theme_bw()

ProcessDataNestGrowth %>%
 unnest(cols = c(OD720_logistic_tidied),names_sep = "_") %>%
  select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, OD720_logistic_tidied_term, OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error)) %>%
  pivot_wider(names_from =  OD720_logistic_tidied_term, values_from = c(OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error), names_sep = "_") %>%
  rename(OD720_Lmax = OD720_logistic_tidied_estimate_Lmax,
         OD720_Lmax_se = OD720_logistic_tidied_std.error_Lmax,
         OD720_Lmu = OD720_logistic_tidied_estimate_Lmu,
         OD720_Lmu_se = OD720_logistic_tidied_std.error_Lmu,
         OD720_Lintercept = OD720_logistic_tidied_estimate_Lintercept,
         OD720_Lintercept_se = OD720_logistic_tidied_std.error_Lintercept) %>%
  mutate(GrowthFlag = if_else((OD720_Lintercept + OD720_Lintercept_se) < ((OD720_Lmax - OD720_Lmax_se) & (OD720_Lmu_se < OD720_Lmu * GrowthFlagError) & (OD720_Lmax_se < OD720_Lmax * GrowthFlagError) ), 1, 0)) %>%
  filter(GrowthFlag != 0) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = OD720_Lmax, colour = as.factor(WL))) +
  #geom_text(data = . %>% filter(GrowthFlag_OD720 == 0), aes(x = Par_ue, y = 0, label = "*")) +
  geom_errorbar(aes(x = Par_ue, ymin = OD720_Lmax - OD720_Lmax_se, ymax = OD720_Lmax + OD720_Lmax_se, colour = as.factor(WL))) + 
  scale_colour_manual(values = MCMIXColours) +
  facet_grid (cols = vars(Strain), rows = vars(O2)) +
  theme_bw()

```




# Save .Rds of ProcessDataNestGrowth containing logistic fits of growth data from time resolved and whole interval fits

```{r}
# saveRDS(object = ProcessDataNestGrowth, file = file.path(DataOut, paste(ProcessFileName,  "ProcessDataNestGrowth.Rds",  sep = "_")), ascii = FALSE, version = NULL, compress = TRUE, refhook = NULL)
# 

```
