---
title: "MultiDataGrowthAssess"
author:
- Laurel Genge
- Carlie Barnhill
- Max Berthold
- Douglas A. Campbell
- Mireille Savoie
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: Prochlorococcus_O2_NPQ.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

## Set figure caption font size
```{css, echo=FALSE}
p.caption {
  font-size: 18px;
}
```

## Set Chunk Options
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```


# Introduction

# Materials and Methods

## Load Libraries and set project variables

```{r load libraries}
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(zoo)
#library(tidyquant)
#library(data.table)
#library(googledrive)
#library(googlesheets4)
#library(dplyr)
```

```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..","ProcessedData", "LogGrowthFits")
PlotsPath <- file.path("..","Plots")
ShinyPath <- file.path("..", "ShinyPico", "data")
DataOut <- file.path("..","GrowthAssessData")
MetaCatalog <- file.path("..","PicoCatalog.csv")



#set the hour of day at which photoperiod starts for later generation of ToD Time of Day
#StartHour <- 6

```

```{r set colours}
MyWavelengths = c(405, 450, 475, 530, 615, 660, 730, "WW")
MCMIXColours = c("violet", "darkblue", "dodgerblue", "green","orange","red","purple", "black")

names(MCMIXColours) <- MyWavelengths
MCMIXColours
```

## List previously processed data

Note: Split files will not be correct for Par_ue, but Actinic_par should be OK Fix: replace MetaData Par_ue with max(Actinic_par) for each file or split file

```{r previous ProcessedData}
ProcessedFiles <- list.files(path = DataIn, pattern = Project, full.names = TRUE)

ProcessedFiles
```

# Read .Rds, Summarize, Combine to single data frame

## Create function using to read in .Rds, adding source filename as a column

```{r readRDS_plus}
readRDS_plus <- function(Flnm){readRDS(file = Flnm) %>%
    mutate(Filename = Flnm)
}
```

## Read in ProcessedFiles .Rds
```{r read selected ProcessedData}

# TestData <- readRDS_plus(Flnm = file.path("../ProcessedData/LogGrowthFits/20200731_PICO_MCMIX004_RUN17_ProcessDataNestGrowth.Rds"))
 
#include "OD720_logistic","deltaOD_logistic" if we need to regenerate predictions for plotting?                                        
LogFitsData <-  ProcessedFiles %>%
    map_df(~readRDS_plus(Flnm = .)) %>%
    select(-c("PrimaryOperator", "Motivation", "doi", "SourceSalinity", "EndDate", "Salinity",  "InocpH", "data", "OD720_logistic","deltaOD_logistic"))

```


# Plot growth rates for each combination of Tube x Filename

```{r plot growth, flag growth}
OD720_unnest <- LogFitsData %>%
unnest(cols = c(OD720_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  OD720_logistic_tidied_term, values_from = c(OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error, OD720_logistic_tidied_statistic, OD720_logistic_tidied_p.value), names_sep = "_")  %>%
  rename(OD720_pmax = OD720_logistic_tidied_estimate_pmax,
         OD720_pmax_se = OD720_logistic_tidied_std.error_pmax,
         OD720_mu = OD720_logistic_tidied_estimate_mu,
         OD720_mu_se = OD720_logistic_tidied_std.error_mu,
         OD720_intercept = OD720_logistic_tidied_estimate_intercept,
         OD720_intercept_se = OD720_logistic_tidied_std.error_intercept) %>%
   mutate(GrowthFlag_OD720 = if_else(!is.na(OD720_pmax) & (OD720_intercept + OD720_intercept_se)  < (OD720_mu - OD720_mu_se)*7, 1, 0))

OD720SummaryGrowthPlot <- OD720_unnest %>%
  # filter(OD720_mu_se < 0.05) %>%
  #  filter(OD720_mu < 0.05) %>%
  filter(OD720_mu_se < 2 * OD720_mu) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = OD720_mu, colour = as.factor(WL))) +
   labs(subtitle = "Strain, O2, Actinic PAR (nm)", y = "Cell Density and Cell Size Specific Exponential Growth Rate (OD720_mu)", x = "Growth Light (µE = µmol photons m-2 s-1)") +
  #geom_text(aes(x = Par_ue, y = OD720_mu, label= Run),hjust=0, vjust=0) +
  geom_errorbar(aes(x = Par_ue, ymin = OD720_mu - OD720_mu_se, ymax = OD720_mu + OD720_mu_se, colour = as.factor(WL))) +
  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
  coord_cartesian(xlim = c (0, 200)) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid (cols = vars(O2, WL), rows = vars(Strain)) +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

OD720SummaryGrowthPlot

ODDelta_unnest <- LogFitsData %>%
unnest(cols = c(deltaOD_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  deltaOD_logistic_tidied_term, values_from = c(deltaOD_logistic_tidied_estimate, deltaOD_logistic_tidied_std.error, deltaOD_logistic_tidied_statistic, deltaOD_logistic_tidied_p.value), names_sep = "_")  %>%
  rename(deltaOD_pmax = deltaOD_logistic_tidied_estimate_pmax,
         deltaOD_pmax_se = deltaOD_logistic_tidied_std.error_pmax,
         deltaOD_mu = deltaOD_logistic_tidied_estimate_mu,
         deltaOD_mu_se = deltaOD_logistic_tidied_std.error_mu,
         deltaOD_intercept = deltaOD_logistic_tidied_estimate_intercept,
         deltaOD_intercept_se = deltaOD_logistic_tidied_std.error_intercept)%>%
   mutate(GrowthFlag_deltaOD = if_else(!is.na(deltaOD_pmax) & (deltaOD_intercept + deltaOD_intercept_se)  < (deltaOD_mu - deltaOD_mu_se)*7, 1, 0)) #Growth flag using deltaOD_pmax instead of _mu usually returned erroneous flag of 0.  


deltaODSummaryGrowthPlot <- ODDelta_unnest %>%
  filter(deltaOD_mu_se < 2 * deltaOD_mu) %>%
  #filter(deltaOD_mu_se < 0.05) %>%
  #filter(deltaOD_mu < 0.05) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = deltaOD_mu, colour = as.factor(WL))) +
  labs(subtitle = "Strain, O2, Actinic PAR (nm)", y = "Chlorophyll Specific Exponential Growth Rate (deltaOD_mu)", x = "Growth Light (µE = µmol photons m-2 s-1)") +
  #geom_text(aes(x = Par_ue, y = deltaOD_mu, label= Run),hjust=0, vjust=0) +
  geom_errorbar(aes(x = Par_ue, ymin = deltaOD_mu - deltaOD_mu_se, ymax = deltaOD_mu + deltaOD_mu_se, colour = as.factor(WL))) + 
  coord_cartesian(xlim = c (0, 200)) + 
  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid (cols = vars(O2, WL), rows = vars(Strain)) +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

deltaODSummaryGrowthPlot


```

```{r plot growth flags}

OD720GrowthFlagPlot <- OD720_unnest %>%
  #filter(deltaOD_mu_se < 2 * deltaOD_mu) %>%
  #filter(deltaOD_mu_se < 0.05) %>%
  #filter(deltaOD_mu < 0.05) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = GrowthFlag_OD720, colour = as.factor(WL), labels = c(Run))) +
  labs(subtitle = "Strain, O2, Actinic PAR (nm)", y = "OD720 Growth Flag (1,0)", x = "Growth Light (µE = µmol photons m-2 s-1)") +
  #geom_text(aes(x = Par_ue, y = deltaOD_mu, label= Run),hjust=0, vjust=0) +
  #geom_errorbar(aes(x = Par_ue, ymin = deltaOD_mu - deltaOD_mu_se, ymax = deltaOD_mu + deltaOD_mu_se, colour = as.factor(WL))) + 
  coord_cartesian(xlim = c (0, 200)) + 
  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
  coord_cartesian(ylim = c (-0.5, 2)) +
  scale_y_continuous(breaks=seq(0, 2, by = 1)) + 
  scale_colour_manual(values = MCMIXColours) +
  facet_grid (cols = vars(O2, WL), rows = vars(Strain)) +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

OD720GrowthFlagPlot

plotly::ggplotly(OD720GrowthFlagPlot)

deltaODGrowthFlagPlot <- ODDelta_unnest %>%
  #filter(deltaOD_mu_se < 2 * deltaOD_mu) %>%
  #filter(deltaOD_mu_se < 0.05) %>%
  #filter(deltaOD_mu < 0.05) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = GrowthFlag_deltaOD, colour = as.factor(WL), labels = c(Run))) +
  labs(subtitle = "Strain, O2, Actinic PAR (nm)", y = "DeltaOD Growth Flag (1,0)", x = "Growth Light (µE = µmol photons m-2 s-1)") +
  #geom_text(aes(x = Par_ue, y = deltaOD_mu, label= Run),hjust=0, vjust=0) +
  #geom_errorbar(aes(x = Par_ue, ymin = deltaOD_mu - deltaOD_mu_se, ymax = deltaOD_mu + deltaOD_mu_se, colour = as.factor(WL))) + 
  coord_cartesian(xlim = c (0, 200)) + 
  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
  coord_cartesian(ylim = c (-0.5, 2)) +
  scale_y_continuous(breaks=seq(0, 2, by = 1)) + 
  scale_colour_manual(values = MCMIXColours) +
  facet_grid (cols = vars(O2, WL), rows = vars(Strain)) +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

deltaODGrowthFlagPlot

plotly::ggplotly(deltaODGrowthFlagPlot)


```


```{r unnest truncated growth data}
OD720trunc_unnest <- LogFitsData %>%
 unnest(cols = c(OD720trunc_logistic_tidied),names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  OD720trunc_logistic_tidied_term, values_from = c(OD720trunc_logistic_tidied_estimate, OD720trunc_logistic_tidied_std.error, OD720trunc_logistic_tidied_statistic, OD720trunc_logistic_tidied_p.value), names_sep = "_") %>%
  rename(OD720trunc_pmax = OD720trunc_logistic_tidied_estimate_pmax,
         OD720trunc_pmax_se = OD720trunc_logistic_tidied_std.error_pmax,
         OD720trunc_mu = OD720trunc_logistic_tidied_estimate_mu,
         OD720trunc_mu_se = OD720trunc_logistic_tidied_std.error_mu,
         OD720trunc_intercept = OD720trunc_logistic_tidied_estimate_intercept,
         OD720trunc_intercept_se = OD720trunc_logistic_tidied_std.error_intercept)

# uncomment after I fix the exp_eqn function
# Unnested_OD720trunc_exp <- LogFitsData %>%
#  unnest(cols = c(OD720trunc_exp_tidied),names_sep = "_", keep_empty = TRUE) %>%
#   pivot_wider(names_from =  OD720trunc_exp_tidied_term, values_from = c(OD720trunc_exp_tidied_estimate, OD720trunc_exp_tidied_std.error, OD720trunc_exp_tidied_statistic, OD720trunc_exp_tidied_p.value),
#   names_sep = "_") %>%
#   rename(OD720trunc_exp_mu = OD720trunc_exp_tidied_estimate_mu,
#          OD720trunc_exp_mu_se = OD720trunc_exp_tidied_std.error_mu,
#          OD720trunc_exp_intercept = OD720trunc_exp_tidied_estimate_intercept,
#          OD720trunc_exp_intercept_se = OD720trunc_exp_tidied_std.error_intercept)

```



```{r save summary growth plots}

ggsave(file = file.path(PlotsPath, paste("OD720SummaryGrowthPlot",".png",sep = "")), plot = OD720SummaryGrowthPlot, device = NULL, scale = 1, height=15, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)

ggsave(file = file.path(PlotsPath, paste("deltaODSummaryGrowthPlot",".png",sep = "")), plot = deltaODSummaryGrowthPlot, device = NULL, scale = 1, height=15, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)


```


# Mirielle to join unnested truncated  growth rates here
```{r compare lndelta to lnOD720 growth rates}
OD720_unnest_test <- OD720_unnest %>%
  select(-c("OD720_logistic_param", "deltaOD_logistic_tidied", "deltaOD_logistic_param"  ))
         
ODDelta_unnest_test <- ODDelta_unnest %>%
  select(-c("OD720_logistic_tidied", "OD720_logistic_param", "deltaOD_logistic_param", "OD720trunc_logistic_tidied", "OD720trunc_logistic_param")) 

# OD720trunc_unnest_test <- OD720trunc_unnest %>%
#   select(-c("OD720trunc_logistic_param", "deltaOD_logistic_tidied", "deltaOD_logistic_param"  ))
  
EvenGrowthLog <- left_join(x = OD720_unnest_test, y = ODDelta_unnest_test)



EvenGrowthLogPlot <- EvenGrowthLog %>% 
  #filter(deltaOD_mu_se < 2 * deltaOD_mu) %>%
  #filter(OD720_logistic_tidied_p.value_mu < 0.05) %>%
  #filter(deltaOD_logistic_tidied_p.value_mu < 0.05) %>%
  ggplot(aes(x = OD720_mu, y = deltaOD_mu, colour = WL)) +
  theme(panel.spacing.x = unit(10, "cm"), panel.spacing.y = unit(2, "cm")) +
  geom_point(aes(labels = c(Run))) +
#geom_errorbar(aes(xmin =  lndeltaODgrowth_tidied_estimate -  lndeltaODgrowth_tidied_std.error, xmax = lndeltaODgrowth_tidied_estimate +  lndeltaODgrowth_tidied_std.error)) +
  scale_colour_manual(values = MCMIXColours) +
  #geom_text(aes(x = OD720_mu, y = deltaOD_mu, label= Run),hjust=0, vjust=0) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  coord_fixed(ratio = 1) +
  coord_cartesian(xlim = c (0, 0.03), ylim = c(0, 0.03)) +
  scale_x_continuous(breaks=seq(0, 0.03, by = 0.01)) +
  labs(subtitle = "Strain, O2, Actinic PAR (nm)", y = "Chlorophyll Specific Exponential Growth Rate (deltaOD_mu)", x = "Cell Density and Cell Size Specific Exponential Growth Rate (OD720_mu)") +
  facet_grid(rows = vars(Strain), cols = vars(O2, WL)) + 
  theme_bw() + 
  labs(colour = "Actinic PAR (nm)")

EvenGrowthLogPlot

plotly::ggplotly(EvenGrowthLogPlot)


```


```{r save Even Growth Plots}
ggsave(file = file.path(PlotsPath, paste("EvenGrowthLogPlot",".png",sep = "")), plot = EvenGrowthLogPlot, device = NULL, scale = 1, height=15, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)

```



```{r save unested growth summaries to ShinyPico}}

# saveRDS(object = EvenGrowthLog, file = file.path(ShinyPath, "PicoGrowthLogs.Rds"), ascii = FALSE, version = NULL, compress = FALSE, refhook = NULL)

# also save RDS file to shiny folder

saveRDS(EvenGrowthLog, file = file.path("ShinyPico", "data", paste(Project, "GrowthLogs", ".Rds",sep = "_"),fsep = .Platform$file.sep))


```


Combine separate growth estimates from mean and s.d. <https://www.statstodo.com/CombineMeansSDs_Pgm.php>

```{r combine estimates by condition}
# SelectedDataGrowthRates %>%
#   group_by(Par_ue, Strain, O2, WL) %>%
```

XXXXX


# Statistical ANOVA to determine effects of WL, O2, Par_ue & Strain on metric of growth rate.

Normally not more than 3 factor ANOVA, so consider running separately for each strain.
